---
title: "My home leaflet mapping"
output: html_document
df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Leaflet Mapping
Here we are mapping the story of my residential accross different states and countries using leaflet` library of mapping functions.

Step1: Installing required packages 1)stringr for string manipulation 2) Leaflet for WebMap & 3) Jsonlite for reading json files
```{r}
suppressPackageStartupMessages({
  if (!require(stringr)){ install.packages("stringr")}; library(stringr)
  if (!require(leaflet)){ install.packages("leaflet")}; library(leaflet)
  if (!require(jsonlite)){ install.packages("jsonlite")}; library(jsonlite)
  })
```

Step2: Load the city.list.json file and convert it into a dataframe.
```{r Json setup}
system.time({cityjson<-jsonlite::fromJSON("city.list.json")})
dim(cityjson)
str(cityjson)
head(cityjson)
city = which(str_detect(cityjson$country, "IN|CN"))
citynew = cityjson[city,]

```

I have completed orbitting sun 30 times and continuing my journey for 31st time. Most memorable moments stay in life comes from Travel/Journey from one place to another and enjoy its diversity.

Though i am home sick, life sometimes gives surprise and throw me away from home.  

Step3: Below, I walk down memory lane and trace those towns and cities which over the decades, I've had privilege of staying.
```{r places}
cities.home <- c("Madurai", "Chennai", "Zhuhai", "Bangalore", 
                 "Hyderabad", "Chennai")

desc.home <- c("born @ 1988", "Studies till @2009", "Business Visit from  Flextronics @ 2016", 
               "Work at Applied Materials @ 2017", "ISB CBA Studies @ 2018",
               "Work at Technosoft @ till now")

cityreq = data.frame(id=integer(), name=character(), country=character(), 
                  coord.lon=numeric(), coord.lat=numeric(), stringsAsFactors=FALSE)

cityreq = citynew[0,] 
cities1 = unique(cities.home)   

# loop in the city details from the city list
for (i1 in 1:length(cities1)){
  a1 = citynew[tolower(citynew$name) == tolower(cities1[i1]),]; 
  a1
  cityreq = rbind(cityreq, a1[1,])
}
cityreq

```

Step4: Extracting Geocodes for the cities
```{r lat-lon extract}
df1 = data.frame(city=cities.home, desc=desc.home)
for (i1 in 1:length(desc.home)){
  a201 = which(cityreq$name == cities.home[i1])
  df1$lon[i1] = cityreq$coord$lon[a201]
  df1$lat[i1] = cityreq$coord$lat[a201]
}
df1
```
Step5: Finding max & min lattitude, Longitude values with small difference for leaflet mapping
```{r}
lng1 = min(df1$lon) - 1; lng1
lng2 = max(df1$lon) + 1; lng2
lat1 = min(df1$lat) - 1; lat1
lat2 = max(df1$lat) + 1; lat2
```
Step6: Mapping
```{r Leaflet Mapping}
mymap = leaflet() %>%
  
 addTiles() %>%
  addProviderTiles("Esri.WorldTopoMap") %>%

  setMaxBounds(lng1, lat1, lng2, lat2) %>%

  addPolylines(data=df1, ~lon, ~lat, color = "black", 
               weight = 2, opacity = 0.6) %>%
  
  addCircleMarkers(data=df1, ~lon, ~lat,  color = "red", 
                   opacity = 0.6, radius = 2, popup = ~paste(df1$city,df1$desc,sep=","))

mymap


```



